Modal Abstractions for Virtualizing Memory Addresses

### 2023-04-04 programlogic.tex
+

  \{ \crthree \mapsto_{r} R1 \ast [r0](a_0 \mapsto_{\textsf{v}}p_0  \ast a_1 \mapsto_{\textsf{v}}p_1)  \ast  b_0 \mapsto_{\textsf{v}}p_3  \ast b_1 \mapsto_{\textsf{v}}p_4 \}
  \end{array}
\]

The choice of resource defining the modal context already exhibits itself as a reasoning principle (Figure \ref{fig:modalcontextinvariance}) in which we can intro/eliminate any resource that is not virtual pointsto into/from modal context without dischargin any obligation. We can use this entailment for  \todo[inline,color=red]{Ask Colin}.

\begin{remark}[The Choice of Modal Context Definition as a Pattern of Verification Context]
  \label{remark:pattern}
  By choosing the contingency and what defines the modal contex, we simply introduce 
  \begin{enumerate}
  \item how a modal context (e.g. a address-space modality $[r]P$), logically, draws the attention to the certain facts in the interest of reasoning (e.g. virtual pointsto relations in the current address-space in Figure \ref{fig:virtualpointstosharing})
  \item and, offloads the burden of individual bookkeeping of these facts (e.g. virtual pointsto relations per address-space) under different context (e.g. virtual pointsto relations in other address-spaces) via utilizing the \textit{summarization} aspect of the contingency it represents (e.g. other virtual pointsto relations are valid under other certain address-space page-table root addresseses).  
  \end{enumerate}
\end{remark}
\paragraph{Interaction}
\label{sec:interaction}

\subsubsection{Address-Space Modality}
\label{sec:aspacemodalist}
The truth on an address space, exhibits itself as a contingent truth: a location virtualization assertion (a virtual points-to in \ref{fig:virtualpointstosharing}),  happens to valid in the \textit{current world} (in the current address space), and switching address spaces pulls information out of one \textit{world} into the “current view” of memory, and leaves other assertions true relative to the previous address space.

>>>>

  \{ \crthree \mapsto_{r} R1 \ast [r0](a_0 \mapsto_{\textsf{v}}p_0  \ast a_1 \mapsto_{\textsf{v}}p_1)  \ast  b_0 \mapsto_{\textsf{v}}p_3  \ast b_1 \mapsto_{\textsf{v}}p_4 \}
  \end{array}
\]
\begin{remark}[The Choice of Modal Context Definition as a Pattern of Verification Context]
  \label{remark:pattern}
  By choosing the contingency and what defines the modal contex, we simply introduce 
  \begin{enumerate}
  \item how a modal context (e.g. a address-space modality $[r]P$), logically, draws the attention to the certain facts in the interest of reasoning (e.g. virtual pointsto relations in the current address-space in Figure \ref{fig:virtualpointstosharing})
  \item and, offloads the burden of individual bookkeeping of these facts (e.g. virtual pointsto relations per address-space) under different context (e.g. virtual pointsto relations in other address-spaces) via utilizing the \textit{summarization} aspect of the contingency it represents (e.g. other virtual pointsto relations are valid under other certain address-space page-table root addresseses).  
  \end{enumerate}
\end{remark}
\paragraph{Interaction}
\label{sec:interaction}
\subsubsection{Address-Space Modality}
\label{sec:aspacemodalist}
The truth on an address space, exhibits itself as a contingent truth: a location virtualization assertion (a virtual points-to in \ref{fig:virtualpointstosharing}),  happens to valid in the \textit{current world} (in the current address space), and switching address spaces pulls information out of one \textit{world} into the “current view” of memory, and leaves other assertions true relative to the previous address space.
